Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Extremely minor changes in section 4.2

SOM is a type of unsupervised neural network inspired by the
topographical organisation of the sensory cortex of human brain
\cite{kohonen1998}. It maps highly dimensional data into a lower
dimensional space where similar data patterns are located in more
adjacent areas on the grid. 
It is a very useful analysis tool for visualising complex data with
high number of variables in a simple geometric plane. Therefore, it
could be used for different tasks such as feature selection and data
clustering and visualisation.

@@

SOM follows an iterative process applied in two stages: First, the
weights of the network are initialized randomly then the n-dimensional
input vectors are presented to the network sequentially so the
distance between the weights of the neurons and the inputs are
computed using the simple Euclidean distance; in the second stage, the
neuron which has the shortest distance with the presented input vector
is updated along with its neighbor neurons. This neuron is called the
best matching unit (BMU). The goal of the learning process is to
minimize the neighborhood distance in the output clusters.

When the learning process is done a visual representation method like
the Unified Distance Matrix, or U-matrix for short, is used to
visualize the distances between neurons in the output space. In the
U-matrix, the distance between adjacent neurons is measured and
assigned different colors. Dark colors between neurons indicate large
distances (boundaries) while light colors represent similar areas
(clusters).

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions (clusters) with high training sample concentration and fewer
where the samples are scarce.  
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ

>>>>

SOM is a type of unsupervised neural network inspired by the
topographical organisation of the sensory cortex of human brain
\cite{kohonen1998}. It maps highly dimensional data into a lower
dimensional space where similar data patterns are located in more
adjacent areas on the grid. 
It is a very useful analysis tool for visualising complex data with
high number of variables in a simple geometric plane. Therefore, it
could be used for different tasks such as feature selection and data
clustering and visualisation. %Pablo: some cite here?

@@

SOM follows an iterative process applied in two stages: First, the
weights of the network are initialized randomly, then the n-dimensional
input vectors are presented to the network sequentially so the
distance between the weights of the neurons and the inputs are
computed using the simple Euclidean distance; in the second stage, the
neuron which has the shortest distance with the presented input vector
is updated along with its neighbor neurons. This neuron is called the
best matching unit (BMU). The goal of the learning process is to
minimize the neighborhood distance in the output clusters.

When the learning process is done a visual representation method like
the Unified Distance Matrix, or U-matrix for short, is used to
visualize the distances between neurons in the output space. In the
U-matrix, the distance between adjacent neurons is measured and
assigned different colors. Dark colors between neurons indicate large
distances (boundaries) while ligh colors represent similar areas
(clusters).

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce.  
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ
